Contextuality and the Born rule in fuzzy quantum theories

### 2017-04-07 prop_letter.tex
prop_letter.tex \paragraph{Quantum IVPM and Real-valued Probability Measure} Updating...

Notice that $\iota_{\infty}\circ\mu_{0}$ has a non-empty core relative
to $\events_{0}$ which is commutative. Recall a commutative sub-event
space reduces quantum IVPMs to classical IVPMs. In general, we haven't
found any classical IVPM has an empty core, and Shapley proved that
a good enough classical IVPM always has a non-empty core.

\begin{thm}[Shapley~\cite{Shapley1971,Grabisch2016}]\label{thm:Shapley}For
every interval-valued probability measure~$\bar{\mu}:\events'\rightarrow\mathscr{I}$,
if the following conditions are true.
\begin{itemize}
\item $\events'$ is commutative, i.e., $\bar{\mu}$ is classical.
\item For all commuting $P_{0},P_{1}\in\events$, we have $\bar{\mu}\left(P_{0}\vee P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)$,
where $P_{0}\vee P_{1}$ is defined to be $P_{0}+P_{1}-P_{0}P_{1}$~\cite{Griffiths2003}.
\end{itemize}
Then, $\mathrm{core}\left(\bar{\mu},\events'\right)\ne\emptyset$.\end{thm}

In the language of core, Gleason's theorem states that $\mathrm{core}\left(\bar{\mu},\events\right)$
has a unique element for any quantum IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}_{\infty}$
when $d\ge3$. However, when we only have finite resources, a quantum
IVPM may be identified to more than one states on different sub-event
spaces. The simplest example add an one extra interval~$\unknown=\left[0,1\right]$
to $\mathscr{I}_{\mathrm{D}}$, and consider $\mathscr{I}_{1}=\left\{ \imposs,\unknown,\necess\right\} $.
Then, 
\begin{equation}
\bar{\mu}_{1}\left(P\right)=\begin{cases}
\necess & \text{, if }P=\mathbb{1}\text{ ;}\\
\imposs & \text{, if }P=\mathbb{0}\text{ ;}\\
\unknown & \text{, otherwise.}
\end{cases}\label{eq:homomorphism-1}
\end{equation}
provides no information about any results so that $\mathrm{core}\left(\bar{\mu}_{1},\events'\right)$
contains every quantum real-valued probability measure on $\events'$.
The following is a more sophisticating example.

@@

>>>>

Notice that $\iota_{\infty}\circ\mu_{0}$ has different core element
relative to different sub-event spaces so that it has an empty core
relative to all projectors~$\events$. When $d\ge3$, if we have
infinite measurement resource and consider $\bar{\mu}:\events\rightarrow\mathscr{I}_{\infty}$,
by Gleason's theorem, $\mathrm{core}\left(\bar{\mu},\events\right)$
has a unique element, i.e., we can always identify a unique state.
However, when we only have finite resources, we usually can only identify
a quantum IVPM to more than one states on different sub-event spaces.
The simplest example add an one extra interval~$\unknown=\left[0,1\right]$
to $\mathscr{I}_{\mathrm{D}}$, and consider $\mathscr{I}_{1}=\left\{ \imposs,\unknown,\necess\right\} $.
Then, the quantum IVPM
\begin{equation}
\bar{\mu}_{1}\left(P\right)=\begin{cases}
\necess & \text{, if }P=\mathbb{1}\text{ ;}\\
\imposs & \text{, if }P=\mathbb{0}\text{ ;}\\
\unknown & \text{, otherwise.}
\end{cases}\label{eq:homomorphism-1}
\end{equation}
provides no information about any results so that $\mathrm{core}\left(\bar{\mu}_{1},\events'\right)$
contains every density matrix. A more sophisticating example is the
following.

@@

Notice that $\iota_{\infty}\circ\mu_{0}$ has a non-empty
core relative to $\events_{0}$ which is commutative. In general,
a commutative sub-event space reduces quantum IVPMs to classical IVPMs.
We haven't found any classical IVPM has an empty core, and Shapley
proved that a good enough classical IVPM always has a non-empty core.

\begin{thm}[Shapley~\cite{Shapley1971,Grabisch2016}]\label{thm:Shapley}For
every interval-valued probability measure~$\bar{\mu}:\events'\rightarrow\mathscr{I}$,
if the following conditions are true.
\begin{itemize}
\item $\events'$ is commutative, i.e., $\bar{\mu}$ is classical.
\item For all commuting $P_{0},P_{1}\in\events$, 
\[
\bar{\mu}\left(P_{0}\vee P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)\textrm{ ,}
\]
where $P_{0}\vee P_{1}=P_{0}+P_{1}-P_{0}P_{1}$~\cite{Griffiths2003}.
\end{itemize}
Then, $\mathrm{core}\left(\bar{\mu},\events'\right)\ne\emptyset$.\end{thm}
